Generating Interactive WebSocket Applications in TypeScript

### 2020-03-09 PLACES_2020/encoding.tex
PLACES: address FZ comments
PLACES: remove conversation thread

\subsubsection{Linear Channel Usage}
\label{section:serverlinear}
\fz{This sentence is confusing and I don't know how to fix.}

Developers writing their implementation using the generated APIs 
enjoy channel linearity by construction.
Our library design prevents the two conditions detailed below:

@@

\paragraph{Unused Channels}
The initial state must be supplied to the session runtime
constructor in order to instantiate a session;
this initial state is defined
in terms of the successor states, which in turn has references to its
successors and so forth.
\fz{It's not the approach, rather than the developer implementation?}

The developer's implementation will cover the terminal state
(if it exists), and the
session runtime guarantees this terminal state will be reached
by construction.

>>>>

\subsubsection{Linear Channel Usage}
\label{section:serverlinear}
Developers writing their implementation using the generated APIs 
enjoy channel linearity by construction.
Our library design prevents the two conditions detailed below:

@@

\paragraph{Unused Channels}
The initial state must be supplied to the session runtime
constructor in order to instantiate a session;
this initial state is defined
in terms of the successor states, which in turn has references to its
successors and so forth.
The developer's implementation will cover the terminal state
(if it exists), and the
session runtime guarantees this terminal state will be reached
by construction.
